Declarative Data Analytic

### 2015-06-15 paper.tex
Minor updates
6/15 update

Existing root cause analysis techniques assume the availability of a known
causality model. However, a network administrator may not have a complete
knowledge of all the causality relationships in the system (Examples?). In
certain cases, the only available information is the logging history of a
system. Therefore, a framework that allows the administrator to easily
create, manipulate and query dependency information is of great help. The
framework should also provide a friendly interface that fits the administrator's
high-level understanding of the system. In addition, the framework should also
enable the administrator to easily carry out root cause analysis, given the
dependency information and the logging history.

@@

>>>>

Existing root cause analysis techniques assume the availability of a known
causality model. However, a network administrator may not have a complete
knowledge of all the causality relationships in the system (Examples?). In
certain cases, the only available information is the logging history of a
system. Therefore, a framework that allows the administrator to easily
create, update, manipulate and query dependency information is of great help. The
framework should also provide a friendly interface that fits the administrator's
high-level understanding of the system. In addition, the framework should also
enable the administrator to easily carry out root cause analysis, given the
dependency information and the logging history.

@@

\paragraph{6/9}

We further discussed about the contributions we can make in our project. It now
seems that a promising direction is to explore efficient interactive causal
relationship generation. The causal relationship may be heterogeneous---that is,
the user can specify causal relationship at different level of granularity. Details can be found in 6/9 meeting slides.

Future steps:

\begin{itemize}
\item Related work survey: Does there exist any work that provides similar
  management?

A: Causality of an event can be modeled as a directed tree. A causality group is a set of
partial order, which can be represented as a DAG. The DAG can be implemented as
an adjacency graph, stored in a database.
\item Low-level operation of a command in the declarative language?

A: 
\begin{itemize}
\item Insert($A \rightarrow B$): check if there is a path such that $B
  \rightarrow A$. If
not, add an adjacency link ($A \rightarrow B$) in the adjacent
graph. Otherwise, raise an error.
\item Delete($A \rightarrow B$): Delete the corresponding link in the adjacency
  graph.
\item Update($A \rightarrow B$ to $A \rightarrow C$): Delete($A \rightarrow B$)
  followed by insert($A \rightarrow C$).
\item Manipulate($A \rightarrow B$): Compose? Should also happen at the event level.
\end{itemize}

\item Details of the work flow: the steps the user could take to finish the
  modeling.
\item Connect SAF with ElasticSearch: decouple SAF from SQLite, and use restful
  api as the query language.
\end{itemize}
